\documentclass[12pt]{article}

%\pdfoutput=1

\usepackage[section]{placeins}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[sorting=none]{biblatex}
\usepackage{subfig}
\usepackage{hyperref}

\hypersetup{
   colorlinks=true,       % false: boxed links; true: colored links
   linkcolor=blue,        % color of internal links
   citecolor=red,         % color of links to bibliography
   filecolor=magenta,      % color of file links
   urlcolor=cyan,           % color of external links
   linktocpage = true,
   }

% if we created names here we can quickly change capitalisation etc.
% varient of delta R
\newcommand{\stoppingdeltar}{\ensuremath{R}}
\newcommand{\ktstoppingdeltar}{\ensuremath{R_{k_T}}}
\newcommand{\distancedeltar}{\ensuremath{\Delta R}}
\newcommand{\eigenidx}[1]{\textbf{#1}}  % eigen equation numbering
\newcommand{\indicatoridx}[1]{\textbf{#1}}  % indicator vector numbering
%b related things, so that we always get the math-mode right
\newcommand{\beau}{\ensuremath{b}}
\newcommand{\bbar}{\ensuremath{\bar{b}}}
\newcommand{\bthing}[1]{\ensuremath{b\text{-#1}}}
% some names for consistent capitalisation
\newcommand{\genkt}{generalised $k_T$}
\def\antikt{anti-$k_T$}
\newcommand{\itercone}{iterative cone}
\newcommand{\spectral}{spectral}
\def\fastjet{{\tt FASTJET}}

\bibliography{spectraljet}   
\graphicspath{{./graphics/}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%BEGINNING OF TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\allowdisplaybreaks[2]
\addtolength\textwidth{2cm}
\evensidemargin 0cm
\oddsidemargin  0cm
\begin{document}


\title{\hfill ~\\[-50mm]
                  \textbf{Spectral Clustering for Jet Physics
                }        }

\author{\\[-5mm]
S. Dasmahapatra\footnote{E-mail: {\tt sd@ecs.soton.ac.uk}} $^{1}$,\
H.A. Day-Hall\footnote{E-mail: {\tt h.a.day-hall@soton.ac.uk}} $^{2,3}$,\
B. Ford\footnote{E-mail: {\tt b.ford@soton.ac.uk}} $^{2}$,\ \\
S. Moretti\footnote{E-mail: {\tt stefano@phys.soton.ac.uk}} $^{2,3}$,\
C.H. Shepherd-Themistocleous\footnote{E-mail: {\tt claire.shepherd@stfc.ac.uk}} $^{3}$
\\ \\
\emph{\small $^1$School of Electronics and Computer Science, University of Southampton,}\\
\emph{\small Southampton, SO17 1BJ, United Kingdom}\\
\emph{\small $^2$School of Physics and Astronomy, University of Southampton,}\\
\emph{\small Southampton, SO17 1BJ, United Kingdom}\\
\emph{\small  $^3$Particle Physics Department, Rutherford Appleton Laboratory,}\\
\emph{\small Chilton, Didcot, Oxon OX11 0QX, United Kingdom}\\[4mm]
}
%
\maketitle
%
\vspace*{-10mm}
%
\begin{abstract}
\noindent
We present a new approach to jet definition as an alternative to methods that exploit kinematic data directly, such as the anti-$k_T$ scheme,
we use the kinematics to represent the particles in an event in a new multidimensional space.
The latter is constituted by the eigenvectors of a matrix of kinematic relations between particles, and the resulting partition is called spectral clustering.
After confirming its Infra-Red (IR) safety, we compare 
its performance to the \antikt{} algorithm in reconstructing relevant final states. 
We base this on Monte Carlo (MC) samples generated from the following processes: 
\(gg\to H_{125\,\text{GeV}} \rightarrow H_{40\,\text{GeV}} H_{40\,\text{GeV}} \rightarrow b \bar{b} b \bar{b}\),
\(gg\to H_{500\,\text{GeV}} \rightarrow H_{125\,\text{GeV}} H_{125\,\text{GeV}} \rightarrow b \bar{b} b \bar{b}\)
and
\(gg,q\bar q\to t\bar t\to b\bar b W^+W^-\to b\bar b jj \ell\nu_\ell\).
Finally, we show that the  results for spectral clustering are obtained without any change in the algorithm's parameter settings, unlike the \antikt{} case, which requires the cone size to be adjusted to the physics process under study.
 \end{abstract}
\thispagestyle{empty}
\vfill
\newpage
%
    \input{spectral_introduction}
    \FloatBarrier
    \input{spectral_theory}
    \FloatBarrier
    \input{spectral_method}
    \FloatBarrier
    \input{spectral_results}
    \FloatBarrier
    \input{spectral_conclusions}
    \FloatBarrier
    \section{Acknowledgements}
We thank A. Chakraborty, 
G. Cerro, 
J. Chaplais, 
S. Jain and 
E. Olaiya for insightful discussions. HAD-H thanks
G.P. Salam for useful advice. 
HAD-H, BF, SM and CHS-T are supported in  in part through the NExT Institute.
SM is also supported by the STFC Consolidated
Grant No. ST/L000296/1. BF is funded by the DISCnet \& SEPnet scholarship schemes.
We finally 
acknowledge the use of the IRIDIS High Performance Computing Facility, and associated
support services, at the University of Southampton, in the completion of this work.

\printbibliography
\end{document}
